% abstract.tex
\begin{abstract}
\noindent This project introduces \textbf{Neura}, an innovative integrated e-learning platform that synthesizes five specialized technological domains into a single, unified, and customizable system for modern technical education. Neura addresses the critical "integration gap" in the current e-learning market by providing native implementations of: adaptive practice powered by Deep Knowledge Tracing (DKT), AI-driven tutoring using Retrieval-Augmented Generation (RAG), secure examination with AI-powered proctoring, source code plagiarism detection using AST-based machine learning, and sandboxed code execution through containerized online judge systems.
\\
\\
\noindent Unlike existing platforms that require institutions to "bolt together" multiple disparate systems—such as Moodle, Respondus, MOSS, and beecrowd—Neura provides all five functions within a single, secure, and scalable architecture. The platform is built on a modern technology stack: .NET 9 backend, React (v19) frontend, Microsoft SQL Server database, and specialized Python services for AI components. Each subsystem is grounded in state-of-the-art research, from DKT models for adaptive learning to RAG architectures for educational chatbots, ensuring both academic rigor and practical effectiveness.
\\
\\
\noindent Neura's architectural synthesis represents a novel contribution to e-learning technology, bridging the gap between general-purpose MOOCs and niche, single-feature tools. The platform enables institutions to deliver high-integrity, customizable technical education without the complexity and security concerns of managing multiple vendor relationships and data silos. Future work will focus on advanced personalization, expanded AI capabilities, and enhanced community features.
\end{abstract}